
\documentclass{anna_cv}


\setname{Dr. Anna Tidstam}{}
\setaddress{Braunschweig/Germany}
\setmobile{+49 160 9348 7922}
\setmail{tidstam@gmail.com}
\setposition{Work Student} %ignored for now
\setlinkedinaccount{https://www.linkedin.com/in/tidstam/} %you can play with color of the template (red is also nice..)
\setgithubaccount{https://github.com/tidstam} %you can play with color of the template (red is also nice..)
\definecolor{coolblack}{rgb}{0.0, 0.18, 0.39}
\setthemecolor{black} %you can play with color of the template (red is also nice..)

\begin{document}
%Set variables
%You can add sections, texts, explanations just by copying the style below. Replace the dummy texts "\lipsum[1][x-x]\par" with actual texts.
%Create header
\headerview
\vspace{1ex}
%Sections
%
% Summary

\addblocktext{Summary}{
\noindent \par{\begin{itemize}
    \item[] Swedish manager living in Germany since 2014. Fond of mixed teams and inclusive leadership. I like making between-sites collaborations efficient and to build up new software teams. 
\end{itemize} }
}
%

% Experience
\section{Experience}
\vspace{0.5em}
    \datedexperience{Northvolt AB}{starts 1st July 2021 / Skellefteå} 
    \explanation{Vice President Digitalization} 
    \explanationdetail{\vspace{0.25em}
    \begin{itemize}
        \item Responsible for software engineering and IT applications for one of the first European Gigafactories, with 40 GWh. Planned start of BMW EV32 C sample production in November 2021, followed by Scania’s PPE battery cell. 
        \item Role responsibility remains similar to the previous position at Northvolt Zwei, but relocated to Sweden and a shorter plan to Start of Production. Member of the Northvolt Ett management team, reporting to President of Northvolt Ett. 
    \end{itemize} 	
            \vspace{0.5em}
    }
    %
    \noindent \datedexperience{Northvolt Zwei GmbH \& Co. KG}{Apr 2020 - Jun 2021 / Braunschweig} 
    \explanation{Vice President Digitalization} 
    \explanationdetail{\vspace{0.25em}
    \begin{itemize}
        \item Responsible for software engineering and IT applications for the Gigafactory called Northvolt Zwei planned in Salzgitter, Germany, as a 50/50 joint venture between Northvolt and VW. Planned start of production in 2024 with VW’s unified battery cell, which is developed by Northvolt Labs in Sweden.
        \item Employee \#2. Member of the Management Team, who with the CEO manages the company culture, operations and long term strategy.
        \item \textbf{IT:} Microsoft partnership (Azure Active Directory, Office 365, Dynamics 365, Power BI, Power Apps, Project, Advanced Threat Protection etc.). Product Lifecycle Management with Siemens Teamcenter PLM. Atlassian suite. Approval and rollout of around 100 IT applications.
        \item \textbf{Software:} Northvolt industrial cloud solution for production data traceability and Manufacturing Execution System, based on Amazon Web Services, GraphQL and RestAPI. Software development for machine connectivity with programming language Go.  Computer vision system developed in-house based on OpenCV. Around 500 repositories in Northvolt organization Github. Production Overall Equipment Effectiveness increased based on data analysis and AI solutions.
        \item Cisco network devices and network management plane from Terraform (Infrastructure as Code).
        \item Participation in design workshops with the Bundesministerium for Environment and the European Commission. This will create a legally binding digital passport for electromobility from 2025.
        \item Northvolt Zwei has stopped all operations the 31st of April, and the company will be transferred to VW on the 30th of June 2021, as announced on the VW Power Day the 15th of March.
    \end{itemize} 	
                \vspace{3cm}
    }
    %
        \noindent \datedexperience{BMW Group}{Dec 2015 - Mar 2020 / München} 
    \explanation{Head of Software Quality and Virtual Validation} 
    \explanationdetail{\vspace{0.25em}
    %
     \begin{itemize}
        \item Responsible for software quality and testing for mPAD, hPAD, uPAD, Minerva, BDC, BCP. This includes software quality rule compliance, compiler warnings, requirement testing, unit testing, software component testing, integration testing as well as ECU testing. Both as quality gate in the CI pipeline, as well as overnight testing and virtual testing in the cloud.
        \item Participation in daily software quality drumbeats, lead by BMW Car IT CEO. Included ECUs: Infotainment, autonomous driving, head unit. Driver to definition of generic software quality KPIs and dashboards.
         \end{itemize} }
            \explanationdetail{
                 \begin{itemize}
        \item Building up an organizational unit with 80 FTEs, including recruitment through Critical Techworks in Portugal as well as nearshore consultants. Supervision of one doctoral student in software quality in collaboration with University of Passau.
        \item ASPICE assessment responsibility for the autonomous driving software platform, including hiring an in-house Quality Manager and managing expert consultants.
        \item Driver of strategic initiative from BMW Group CEO to virtualize the ECU testing, in order to reduce the cost for testing but also to scale testing faster. ECUs: xPAD and BCP.
        \item Annual budget responsibility: €10 million, mainly consisting of hardware for test setups and consultancy fees.
    \end{itemize} 	
    }
    \explanation{Manager for Strategical ECU Projects} 
    \explanationdetail{\vspace{0.25em}
     \begin{itemize}
        \item Building up a 50 FTE cross-functional project organization responsible for avoiding critical software quality issues. Fostering a culture of transparency and collaboration.
        \item Replacing the ECU calibration tool-chain,  consisting of around 30 applications. This led to migration of terabytes of version-controlled data as well as new everyday tools for hundreds of engineers. ISO 27001 assessment of new toolchain.
        \item Driver of strategic initiative from BMW Group CEO to virtualize the ECU testing, in order to reduce the cost for testing but also to scale testing faster. ECUs: Vertical and lateral vehicle dynamics.
    \end{itemize} 	
    \vspace{0.5em}
    }
    %
      \noindent \datedexperience{Thermo Fisher Scientific}{Jul 2014 - Dec 2015 / München} 
    \explanation{IT Specialist for Engineering Systems} 
    \explanationdetail{\vspace{0.25em}
        \begin{itemize} 
            \item  Responsible for 30 engineering applications, for example Agile PLM, Windchill and Catia. Starting up global task force teams in order to take advantage of the competence from the IT Head Quarters in Sunnyvale, California. 
        \end{itemize} 	
        \vspace{0.5em}
    }
    %
      \noindent \datedexperience{Mercedes-Benz Technology Center}{Sep 2012 - Nov 2012 / Stuttgart} 
    \explanation{Research collaboration} 
    \explanationdetail{\vspace{0.25em}
         \begin{itemize} 
            \item Design of the product change process between Daimler and Renault for the new Smart / Renault Clio. Implementing an AI support for configuration change management.  
        \end{itemize} 	
        \vspace{0.5em}
        }
    %
     \noindent  \datedexperience{Volvo Trucks}{Nov 2008 - Mar 2010 / Gothenburg} 
    \explanation{Process \& IT Project management} 
    \explanationdetail{\vspace{0.25em}
            \begin{itemize} 
                \item Development of a configurator based on AI. Access to new technology from the collaboration with Chalmers University of Technology.
            \end{itemize} 	
        \vspace{0.5em}
        }
    %
     \noindent  \datedexperience{Pininfarina}{Apr 2007 - Sep 2007 / Turin} 
    \explanation{Master Thesis student} 
    \explanationdetail{\vspace{0.25em}
        \begin{itemize} 
            \item Title “Target setting in the Automotive Product Development”, which was the BEV target setting from a benchmark database. Vehicle: B Zero.
        \end{itemize} 
                \vspace{2cm}
        }
%
%Education
\section{Education} 
\vspace{0.5em}
    \datedexperience{Quantic School of Business and Technology}{Jan 2019 - Jan 2020 / Washington DC} 
    \explanation{Executive MBA} 
     \explanationdetail{\vspace{0.25em}
        \begin{itemize}
        \item Entrepreneurship, Corporate Strategy and Innovations. 
        \item Master Thesis done with peers from Google, European Central Bank and Visteon: https://youtu.be/SExYg4ZvC0c
        \end{itemize} 
        \vspace{0.5em}
     }
    \datedexperience{Chalmers University of Technology}{Feb 2009 - Apr 2014 / Gothenburg \& Stuttgart} 
    \explanation{PhD in Product Development} 
    \explanationdetail{\vspace{0.25em}
            \begin{itemize}
            \item Thesis title: “Efficient Development of Vehicle Configuration Rules”.
Comparison of five automotive OEMs concerning how AI algorithms could increase the data quality in their PLM system.
        \end{itemize} 
        \vspace{0.5em}
     }
         \datedexperience{Chalmers University of Technology}{Aug 2007 - Mar 2014 / Gothenburg} 
    \explanation{M.Sc. Automotive Industrial Design Engineering} 
    \explanationdetail{\vspace{0.25em}
            \begin{itemize}
            \item Second master’s degree. GPA 4.4/5 (Top 10\%).
            \item Sketching, Design Thinking, UI/UX, Marketing, Brand Management.
        \end{itemize} 
        \vspace{0.5em}
     }
              \datedexperience{Chalmers University of Technology}{Aug 2003 - Aug 2008 / Gothenburg} 
    \explanation{B.Sc.and M.Sc. Physics} 
    \explanationdetail{\vspace{0.25em}
            \begin{itemize}
            \item Class instructor in Java development. 
            \item Exchange studies at École Polytechnique in Paris.
        \end{itemize} 
        \vspace{0.5em}
     }
                   \datedexperience{École Polytechnique}{Aug 2006 - Apr 2007 / Paris} 
    \explanation{Exchange semesters} 
    \explanationdetail{\vspace{0.25em}
            \begin{itemize}
            \item Applied Mathematics, Computer Science
        \end{itemize} 
        \vspace{0.5em}
     }
%
% Skills
\section{Skills}
\vspace{0.5em}
    %
    \newcommand{\skillone}{\createskill{Programming Languages}{\textbf{\emph{Experienced:}} \ \  Java  \ \ \textbf{\emph{Familiar:}} \ \  Golang \cpshalf C++ \cpshalf LaTeX}}
    %
    \newcommand{\skilltwo}{\createskill{Software Development}{Algorithms \cpshalf GitHub \cpshalf Agile Methodology}}
    %
    \newcommand{\skillthree}{\createskill{Languages}{\textbf{\emph{Native:}} \ \  Swedish \ \ \textbf{\emph{Fluent:}} \ \ English \cpshalf  German \ \ \textbf{\emph{Beginner:}} \ \  Italian \cpshalf  French }}
    %
    \createskills{\skillone, \skilltwo, \skillthree}
%
% Experience
\section{Extra}
\vspace{0.5em}
    \explanationdetail{\vspace{0.25em}
\begin{itemize}
    \item [] 2020 - Leadership Program, Yale School of Management	
    \item [] 2019 - Digital Transformation, Boston Consulting Group
    \item [] 2018 - Agile Certified Practitioner, PMI
    \item [] 2016 - Coaching skills for managers, University of California
    \item [] 2015 - Project Management Professional (PMP) certification, PMI
\end{itemize}
}

%
%Footnote
\createfootnote
\end{document}
